Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-14 README.Rmd
updated readme with cover letter folder

- Write cover letter
- Finish filling in questions in ASA submission document
- Figure out discrepancies with old and new versions of the training data
- Rerun the lime explanations with the finalized training data
- Edit dataset descriptions in README and add to the readme.txt document for submission
- Update all files in the submission folder
- Upload the files for submission and submit
- Look into using renev

@@

>>>>

- Figure out discrepancies with old and new versions of the training data
- Finish filling in questions in ASA submission document
- Rerun the lime explanations with the finalized training data
- Edit dataset descriptions in README and add to the readme.txt document for submission
- Update all files in the submission folder
- Upload the files for submission and submit
- Look into using renev

@@

**`cover-letter`**

Contains the files associated with the cover letter submitted to the ASA Data Science journal.
